---
title: 'Models & Inference SNA Badge'
subtitle: "LASER Institute SNA Independent Practice"
author: "Dr. Shaun Kellogg"
date: "`r format(Sys.Date(),'%B %e, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Overview

The final activity for each learning lab provides space to work with data (ideally your own) and to reflect on how the concepts and techniques introduced in each lab might apply to your own research. To earn a badge for each lab, you are required to respond to a set of prompts in Part I designed to help assess your understanding of key concepts and to help you think about potential next steps for your own study. In Part II, you will create a simple data product in R that demonstrates your ability apply a data analysis technique introduced in this learning lab.

### Part I: Comprehension Check

Take a look at the article from our case study by Daly and Finnigan (2011), *The Ebb and Flow of Social Network Ties Between District Leaders Under High-Stakes Accountability*, and answer the following questions:

1.  What research questions were the authors of this study trying to address and why did they consider these questions important?

    -   YOUR RESPONSE HERE

2.  What statistical models were employed in this study to address these research questions and what were the results of these analyses?

    -   YOUR RESPONSE HERE

Now think about a network that you are a part of, or may be interested in studying and answer the following questions:

3.  What is a research question that you might ask about this network that a statistical model for networks (e.g. QAP, P\*, etc.) might help to address?

    -    YOUR RESPONSE HERE

4.   What model would be most appropriate for addressing this question and why?

    -   YOUR RESPONSE HERE

### Part II: Data Product 

In our SNA Lab 4 Case Study, we only scratched the surface on the number of network and node attributes properties that can be tested using ERGMs. Take a look at a [table of common ergm-terms](http://statnet.org/nme/d2-ergmterms.html) or type "ergm-terms" into the help menu of the files pane for some additional examples.

Using one of the data sets provided for our case study, or your own data set if you're feeling really ambitious, **your goal for this lab is to extend the ERGM analysis from our case study by adding a new parameter/term to our model.** For example, you may be interested in examining shared characteristics among school leaders might help explain tie formation, such as gender, level of trust in colleagues, or whether they work at the school or district level.

I highly recommend creating a new R script in your `lab-4` folder to complete this task. When your code is ready to share, use the code chunk below to share the final code for your model and answer the questions that follow.

```{r, my-data-product}
# YOUR FINAL CODE HERE


```

1.  

### 🧶 Knit & Submit 

1.  **Share your data product.** When you feel you've wrangled and analyzed the data to your satisfaction, create an R Markdown file that includes a polished sociogram and/or data table and a narrative highlighting your research question, data source, and key findings and potential implications. Your R Markdown file should include a polished sociogram and/or table, a title and narrative, and all code necessary to read, wrangle, and explore your data.

2.  **Share your product.** Knit your data product to a desired output format. This may be a simple [HTML](https://bookdown.org/yihui/rmarkdown/html-document.html), [PDF](https://bookdown.org/yihui/rmarkdown/pdf-document.html), or [MS Word](https://bookdown.org/yihui/rmarkdown/word-document.html) file; or something more complex like [HTML5 slides](https://bookdown.org/yihui/rmarkdown/ioslides-presentation.html), a [Tufte-style handout](https://bookdown.org/yihui/rmarkdown/tufte-handouts.html), [dashboard](https://rmarkdown.rstudio.com/flexdashboard/), or [website](https://bookdown.org/yihui/rmarkdown/rmarkdown-site.html). Then create a new discussion post below to share your analysis. Include in the post your published web link (e.g., via [RPubs](https://rpubs.com/about/getting-started) or [GitHub](https://towardsdatascience.com/how-to-create-a-free-github-pages-website-53743d7524e1)) or attached file (e.g. HTML or PDF) and add a short reflection including one thing you learned and one thing you'd like to explore further.
